\def\x#1{\ \hbox to 1.3in{\hss \bf #1}\ $\cdot$}

\voffset -0.5in
\vsize 10in
\hoffset -0.5in
\hsize 7.5in
\parindent 0pt
\nopagenumbers
\frenchspacing

\setbox100=\vbox{\obeylines\parskip=4pt\hsize=0.475\hsize
  \x{Alternade} $A, B, \Sigma_ia_ib_i$ (compare Interlock)
  \x{Alterposal} $A, \widetilde{\Sigma_ia_{2i}}, \widetilde{\Sigma_ia_{2i+1}}$
  \x{Antiposal} $A, B, \widetilde{AB}; A\approx -B$ ($A,B$ overloaded)
  \x{Backswitch} $Ab, \overleftarrow A c$ (compare Switchback)
  \x{Baltimore Deletion} $A, \forall_i{A\backslash a_i}$
  \x{Baltimore Transdeletion} $A, \forall_i\widetilde{A\backslash a_i}$
  \x{Beheadment} $aB, B$
  \x{Change 'n' Swap} $AbC, CdA$
  \x{Change of Heart} $ABC, DEF, AEC, DBF$
  \x{Changeover} $AbCD, ACeD$
  \x{Charade} $ABC..., A, B, C, ...$
  \x{Chop 'n' Swap} $AbC, CA$
  \x{Curtailment} $Ab, A$
  \x{Cyclegram} $AB, BC, ... CA$
  \x{Deletion} $AbC, AC$
  \x{Double-Cross} $AB, CD, AD, CB$
  \x{Dropout} $ABC, DEF, ACDF, BE$
  \x{Hack 'n' Back} $AbC, A\overleftarrow C$
  \x{Head-to-tail Shift} $aB, Bc$
  \x{Heart Transplant} $ABC, DE, AC, DBE$
  \x{Heteronym} $A, A^\prime$
  \x{Interlock} $A, B, \Sigma_iA_iB_i$ (compare Alternade)
  \x{Letter Bank} $A, \{A\}...$ ($A$'s letters are unique)
  \x{Letter Change} $AbC, AdC$
  \x{Letter Shift} $AbCD, ACbD$
  \x{Linkade} $Ab, bC, AC$
  \x{Metathesis} $AbCdE, AdCbE$
  \x{Mynoreteh} $A, \overleftarrow{A^\prime}$
  \x{Padlock} $AB, BC, AC$
  \x{Palindrome} $Ab\overleftarrow A$ ($b$ may be void)
  \x{Pasteover} $AbCdE, AdCE$ or $AbCdE, ACbE$
  \x{Popover} $AbCdE, AdCfE$ (or variants)
  \x{Reversal} $A, \overleftarrow A$
  \x{Reduplication} $A, AA$
  \x{Split Shift} $ABC, ADC, ... BD$
  \x{Switchback} $aB, c\overleftarrow B$ (compare Backswitch)
  \x{Synoposal} $A, B, \widetilde{AB}; A\approx B$ ($A,B$ overloaded)
  \x{Terminal Deletion} $aBc, B$
  \x{Terminal Rotation} $aBc, dEf, fBa cEd$
  \x{Transade} $ABC..., \tilde A, \tilde B, ...$
  \x{Trans-cross} $AB, CD, AC, BD$
  \x{Transdeletion} $AbC, \widetilde{AC}$
  \x{Transpogram} $AB, BA$
  \x{Transposal} $A, \tilde A$
  \x{Transubstitution} $ AbC, \widetilde{AdC}, ...$
  \x{Word Deletion} $ABC, AC, B$
  \x{Word Substitution} $ABC, B, D, ADC$
}

\hbox to \hsize{\vsplit 100 to 0.5\ht100\hfill \box 100}
\parskip=4pt

{\bf A/D/T Enigmas:} {\bf Acrostical} has fragments at the start of each
stanza; {\bf Telestical} at the end; {\bf Diastichal} in the middle
(and must use at least 1 letter on one side and 2 on the other). {\bf
  Acrotelestichal} has fragments at the start {\it and} end of each
stanza, read in order $A_1T_1A_2T_2...$ {\bf Reversed} applies to the
answer before division.

{\bf Spoonergram} swaps initial sounds (including possibly null) at
the start of two words.

{\bf Isogram} has two or more answers which can be cryptograms of one
another. {\bf Consonantcy} has two or more answers with the same
consonants in the same order. {\bf Vowelcy} ... same vowels.... (Y is
always considered a vowel.)

{\bf Literatim} has numbered cuewords whose answers are homophones of
the letters in the corresponding position of the answer.

{\bf Phrase Shift} is a {\bf Letter Shift} on a well-known phrase,
which is not given a cueword but which is often implied contextually.

{\bf Rebus and friends}. The basic rebus: The answer phrase can be
re-parsed as the reading which literally describes the characters in
the rubric. {\bf Enigmatic} rebi eliminate the ``literally''. In a
{\bf Suber} the reading is a reversal of the solution. In a {\bf
Rebade} the reading is an alternade of the sol. (I write the sol
horizontally in $C$ columns $\times$ $R$ rows and then read the
reading downwards in $R$ rows $\times$ $C$ columns.) In a {\bf Subade}
the reading is reversed as in a suber, then alternaded.

{\bf Group} flats apply the same type of wordplay (but not with the
same arguments) to words that form a familiar group. The group itself
is not enumerated or part of the sol.

\vskip 6pt
\hrule 
\vskip 4pt

\hbox to \hsize{\hss Version 1.1.0 --- 22 Jan 2024 --- Copyright \copyright\ 2024 Andrew Marc Greene. May be shared under CC-BY-SA \hss}
% Changelog:
% 1.0.1 - fixed error in Heart Transplant (thanks, Bonedog!)
% 1.0.2 - fixed errors in Baltimore (Trans)deletion, double-cross (thanks, Wild Rice!)
% 1.1.0 - added antiposal, synoposal

\bye
